---
title: "PCR Test Result Delay"
author:
- name: Nicole Harty, MPH
  affiliation: Epidemiologist/Data Manager
date: "`r format(Sys.time(), '%B %d, %Y, %I %p')`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 5
    css: template.css
---

# All Cases Summary   
This section summarizes the demographics of Routt County cases by providing both the totals for all cases as well as a summary for the last two weeks' cases. Statistics for all cases to date are compared to the Routt County population.  

## Age  
Most Recent Two Weeks: **`r format((as.Date(params$DataThroughDate))-days(13),'%B %d, %Y')` through `r as.Date(params$DataThroughDate) %>% format('%B %d, %Y')`**.  
  
```{r label=Age2WeeksAllCasesCountyCompare}
ConfProbCases %>%
  # filter(CountsTowardTotal=="Yes") %>%
  group_by(AgeGrouping) %>%
  summarise(NumberCases = n()) %>%
  right_join(data.frame(AgeGrouping=
                          c("0-9", "10-19", "20-29", "30-39", "40-49", "50-59", "60-69", "70-79", "80-89", "90+")),
             by = c("AgeGrouping")) %>%
  group_by(AgeGrouping) %>%
  replace(., is.na(.), 0) %>%
  arrange(AgeGrouping) %>%
  mutate(PercentAllCases=round((NumberCases/(ConfProbCases %>%
                                        filter(AttributionDate<=(params$DataThroughDate)) %>%
                                        count() %>%
                                        pull()))*100,2),
         text=paste0("Age Grouping: ",AgeGrouping,"<br>Percentage: ",PercentAllCases,"<br>Case Count: ",NumberCases)) %>%
plot_ly(x = ~AgeGrouping,
  y = ~PercentAllCases,
  type = "bar",
  color = I("#BB4628"),
  name = "All Cases",
  text = ~text,
  hoverinfo = "text") %>%
  add_trace(data = data.frame(Pop=c(2603,3195,2834,4223,3919,3308,3270,1937,553,109), 
                              AgeGrouping=as.factor(c("0-9","10-19","20-29","30-39","40-49","50-59","60-69","70-79","80-89","90+"))) %>%
              mutate(PopPercent=round((Pop/25951)*100,2),
                     text=paste0("Age Grouping: ",AgeGrouping,"<br>Percentage: ",PopPercent,"<br>Case Count: ",Pop)),
            x = ~AgeGrouping,
            y = ~PopPercent,
            type = "bar",
            color = I("#4E2B1F"),
            name = "Routt County Population",
            text = ~text,
            hoverinfo = "text"
              ) %>%
  add_trace(data = ConfProbCases %>%
              filter(
                # CountsTowardTotal=="Yes", 
                IsMostRecent2WeeksRolling=="Yes") %>%
              group_by(AgeGrouping) %>%
              summarise(NumberCases2Weeks = n()) %>%
              right_join(data.frame(AgeGrouping=
                                      c("0-9", "10-19", "20-29", "30-39", "40-49", "50-59", "60-69", "70-79", "80-89","90+")),
                         by = c("AgeGrouping")) %>%
              group_by(AgeGrouping) %>%
              replace(., is.na(.), 0) %>%
              arrange(AgeGrouping) %>%
              mutate(Percent2WeekCases=round((NumberCases2Weeks/(ConfProbCases %>%
                                                                   filter(IsMostRecent2WeeksRolling=="Yes") %>%
                                                                   count() %>%
                                                                   pull()))*100,2),
                     text=paste0("Age Grouping: ",AgeGrouping,"<br>Percentage: ",Percent2WeekCases,"<br>Case Count: ",NumberCases2Weeks)),
            x = ~AgeGrouping,
            y = ~Percent2WeekCases,
            type = "bar",
            name = "Most Recent Two Weeks' Cases",
            color = I("#477691"),
            text = ~text,
            hoverinfo = "text"
              ) %>%
  layout(margin = list(t = 45),
         title = list(text = "Age Distribution All Cases and Most Recent \n Two Weeks' Cases Compared to Routt County Population",
                      yref = "container",
                      yanchor = "top",
                      pad = list(t = 15),
                      y = 1),
         xaxis = list(title = "Age Group"),
         yaxis = list(title = "Percentage"),
         legend = list(orientation = 'h', y=-.25),
         font = list(family = "Arial", size = 12))

```


## Gender  

```{r label=CollapseGenderLevels}
ConfProbCases$gender <- fct_collapse(ConfProbCases$gender, "Unknown, Missing, or Supressed" = c("Male to Female", "Female to Male", "Unknown"))
```

```{r label=GenderCasesPieChart2weeks}
plot_ly() %>%
  add_pie(data = ConfProbCases %>%
            filter(IsMostRecent2WeeksRolling=="Yes") %>%
            group_by(gender) %>%
            count(),
          labels = ~gender, values = ~n,
          marker = list(colors = c('#4E2B1F', '#BB4628', "#477691")),
          name = "Cases",
          title = "Cases",
          domain = list(row = 0, column = 0)) %>%
  layout(margin = list(t=35,b=15),
         title = list(text =  paste0("<b>Most recent two reporting weeks: </b><br>",format((as.Date(params$DataThroughDate)-13),'%B %d, %Y')," through ",
                              format(as.Date(params$DataThroughDate),'%B %d, %Y')),
                      font = list(family = "Arial", size = 14),
                      yref = "container",
                      yanchor = "top",
                      pad = list(t = 10),
                      y = 1
                      ),
         height = "350",
         width = "500")
```
```{r label=GenderCasesPieChartAll}
plot_ly() %>%
  add_pie(data = ConfProbCases %>%
            filter(AttributionDate<=(params$DataThroughDate)) %>%
            group_by(gender) %>%
            count(),
          labels = ~gender, values = ~n,
          marker = list(colors = c('#4E2B1F', "#477691", '#BB4628')),
          name = "Cases",
          title = "Cases",
          domain = list(row = 0, column = 0)) %>%
  add_pie(data = data.frame(Pop=c(12291,13393), gender=as.factor(c("Female","Male"))),
          labels = ~gender, values = ~Pop,
          marker = list(colors = c('#4E2B1F','#BB4628')),
          sort = FALSE,
          name = "Population",
          title = "Population",
          domain = list(row = 0, column = 1)) %>%
  layout(margin = list(t=25,b=15),
         title = list(text = "Gender Breakdown of COVID-19 Cases Compared to Routt County Population",
                      font = list(family = "Arial", size = 14)),
         grid=list(rows=1, columns=2))
```


## Geographic Distribution of Cases  
Cases are attributed based upon address provided when tested and subsequently interviewed. Data may be skewed due to the use of PO Boxes.    
 
```{r label=GeoCasesPerCapita}
ConfProbCases %>%
  mutate(ZIP = str_sub(zipcode, 1,5),
         ZIPgroup = case_when(ZIP %in% c("80428", "80467", "80469", "80477", "80479", "80483", "80487", "80488", "81639") ~ "Routt",
                              TRUE ~ as.character("Incomplete")),
         City = case_when(ZIP %in% c("80477", "80487", "80488") ~ "Steamboat Springs",
                          ZIP=="80428" ~ "North Routt",
                          ZIP=="80467" ~ "South Routt",
                          ZIP=="80469" ~ "South Routt",
                          ZIP=="80479" ~ "South Routt",
                          ZIP=="80483" ~ "South Routt",
                          ZIP=="81639" ~ "West Routt",
                          TRUE ~ as.character("Incomplete"))) %>%
  group_by(City) %>%
  filter(AttributionDate<=(params$DataThroughDate)) %>%
  summarise(NumberCases = n()) %>%
  left_join(data.frame(City=c("North Routt", "South Routt", "West Routt", "Steamboat Springs"),
                        Pop=c(706,3194,2463,17212)),
             by = c("City")) %>%
  mutate(TotalCases = ConfProbCases %>%
           filter(!is.na(zipcode)) %>%
           count() %>%
           pull(),
         TotalPop = 23509,
         CasesPerCapita = round(NumberCases/Pop,4)*100000) %>%
plot_ly(x = ~City, 
        y = ~CasesPerCapita,
        name = "Cases",
        type = "bar",
        marker = list(color = "#BB4628")) %>%
  layout(title = "Per Capita Cumulative Incidence",
         xaxis = list(title = "City"),
         yaxis = list(title = "Incidence Rate per 100,000"),
         shapes = list(
              list(type = 'line',
                   xref = 'paper', x0=0, x1=1,
                   yref = 'y', y0=(ConfProbCases %>%
                                     count() %>%
                                     mutate(CummInc=round((n/params$RouttPop)*100000,2)) %>%
                                     pull(CummInc)), y1=(ConfProbCases %>%
                                                           count() %>%
                                                           mutate(CummInc=round((n/params$RouttPop)*100000,2)) %>%
                                                           pull(CummInc)),
                   line = list(color = '#4E2B1F'))),
         annotations = list(
           list(x = .5,
                y = (ConfProbCases %>%
                                     count() %>%
                                     mutate(CummInc=round((n/params$RouttPop)*100000*1.03,2)) %>%
                                     pull(CummInc)),
                text = "Routt County Cumulative Incidence",
                xref = "paper",
                yref = 'y',
                showarrow = FALSE)),
         font = list(family = "Arial", size = 12))

```

```{r label=GeoCasesPerCapitaRecentMonth}
ConfProbCases %>%
  mutate(ZIP = str_sub(zipcode, 1,5),
         ZIPgroup = case_when(ZIP %in% c("80428", "80467", "80469", "80477", "80479", "80483", "80487", "80488", "81639") ~ "Routt",
                              TRUE ~ as.character("Incomplete")),
         City = case_when(ZIP %in% c("80477", "80487", "80488") ~ "Steamboat Springs",
                          ZIP=="80428" ~ "North Routt",
                          ZIP=="80467" ~ "South Routt",
                          ZIP=="80469" ~ "South Routt",
                          ZIP=="80479" ~ "South Routt",
                          ZIP=="80483" ~ "South Routt",
                          ZIP=="81639" ~ "West Routt",
                          TRUE ~ as.character("Incomplete")),
         PriorCompleteMonth = case_when(year(AttributionDate)==year(Sys.Date())&
                                          month(AttributionDate)==(month(Sys.Date())-1) ~ "Yes",
                                        month(Sys.Date())==1&
                                          month(AttributionDate)==12&
                                          year(AttributionDate)==(year(Sys.Date())-1) ~ "Yes",
                                        TRUE ~ as.character("No"))
         ) %>%
  group_by(City) %>%
  filter(PriorCompleteMonth=="Yes") %>%
  summarise(NumberCases = n()) %>%
  left_join(data.frame(City=c("North Routt", "South Routt", "West Routt", "Steamboat Springs"),
                        Pop=c(706,3194,2463,17212)),
             by = c("City")) %>%
  mutate(TotalCases = ConfProbCases %>%
           filter(!is.na(zipcode)) %>%
           count() %>%
           pull(),
         TotalPop = 23509,
         CasesPerCapita = round(NumberCases/Pop,4)*100000) %>%
plot_ly(x = ~City, 
        y = ~CasesPerCapita,
        name = "Cases",
        type = "bar",
        marker = list(color = "#BB4628")) %>%
  layout(title = "Per Capita Incidence Rate, Most Recent Complete Month",
         xaxis = list(title = "City"),
         yaxis = list(title = "Incidence Rate per 100,000"),
         shapes = list(
              list(type = 'line',
                   xref = 'paper', x0=0, x1=1,
                   yref = 'y', y0=(ConfProbCases %>%
                                     mutate(PriorCompleteMonth = case_when(year(AttributionDate)==year(Sys.Date())&
                                                                             month(AttributionDate)==(month(Sys.Date())-1) ~ "Yes",
                                                                           month(Sys.Date())==1&
                                                                             month(AttributionDate)==12&
                                                                             year(AttributionDate)==(year(Sys.Date())-1) ~ "Yes",
                                                                           TRUE ~ as.character("No"))) %>%
                                     filter(PriorCompleteMonth=="Yes") %>%
                                     count() %>%
                                     mutate(CummInc=round((n/params$RouttPop)*100000,2)) %>%
                                     pull(CummInc)), y1=(ConfProbCases %>%
                                                           mutate(PriorCompleteMonth=
                                                                    case_when(year(AttributionDate)==year(Sys.Date())&
                                                                                month(AttributionDate)==(month(Sys.Date())-1) ~ "Yes",
                                                                              month(Sys.Date())==1&
                                                                                month(AttributionDate)==12&
                                                                                year(AttributionDate)==(year(Sys.Date())-1) ~ "Yes",
                                                                              TRUE ~ as.character("No"))) %>%
                                                           filter(PriorCompleteMonth=="Yes") %>%
                                                           count() %>%
                                                           mutate(CummInc=round((n/params$RouttPop)*100000,2)) %>%
                                                           pull(CummInc)),
                   line = list(color = '#4E2B1F'))),
         annotations = list(
           list(x = .5,
                y = (ConfProbCases %>%
                       mutate(PriorCompleteMonth = case_when(year(AttributionDate)==year(Sys.Date())&
                                                               month(AttributionDate)==(month(Sys.Date())-1) ~ "Yes",
                                                             month(Sys.Date())==1&
                                                               month(AttributionDate)==12&
                                                               year(AttributionDate)==(year(Sys.Date())-1) ~ "Yes",
                                                             TRUE ~ as.character("No"))) %>%
                       filter(PriorCompleteMonth=="Yes") %>%
                       count() %>%
                       mutate(CummInc=round((n/params$RouttPop)*100000*1.03,2)) %>%
                       pull(CummInc)),
                text = "Routt County Incidence",
                xref = "paper",
                yref = 'y',
                showarrow = FALSE)),
         font = list(family = "Arial", size = 12))

```

## Table of Cases  
Click "Download" to download this table as a PDF, Excel or CSV file.  
This table includes all confirmed cases and all probable cases.  
```{r label=WebsiteSpreadsheetPrep, results='hide'}
#include probables for which there is a positive antigen, but not other probables
WebsiteCasesTablePrep <- expand_grid(#AgeGrouping = c("0-9","10-19","20-29","30-39","40-49","50-59","60-69","70-79","80-89","90+"), 
                                     AttributionDate = Calendar$date)

WebsiteCasesTable <- ConfProbCases %>%
  select(eventid, casestatus, reporteddate, gender, AgeGrouping, ReportedDateWeek, ReportedWeekStart, CollectionDateWeek,
         CollectionWeekStart, IsMostRecent2Weeks, AttributionDate) %>%
  group_by(AttributionDate) %>%
  summarise(NumberCases = n()) %>%
  right_join(WebsiteCasesTablePrep, by = "AttributionDate") %>%
  arrange(AttributionDate) %>%
  replace(., is.na(.), 0) %>%
  filter(AttributionDate<=(params$DataThroughDate)) 

# # custom table container for website table
# WebsiteTableSketch = htmltools::withTags(table(
#   class = 'display',
#   thead(
#     tr(
#       th(rowspan = 2, 'Date'),
#       th(colspan = 11, 'Female'),
#       th(colspan = 11, 'Male'),
#       th(rowspan = 2, "Grand Total")
#     ),
#     tr(
#       lapply(rep(c('0-9','10-19','20-29','30-39','40-49','50-59','60-69','70-79','80-89','90+','Total'), 2), th)
#     )
#   )
# ))
# print(WebsiteTableSketch)
```
``` {r label = createwebsitetable}
WebsiteCasesTable %>%
  rename("Date" = "AttributionDate") %>%
  DT::datatable(
    #container = WebsiteTableSketch,
    rownames = FALSE,
    extensions = 'Buttons', 
    options = list(
      dom = 'Bfrtip',
      pageLength = 10,
      scrollX = TRUE,
      buttons = list(
        'copy', 'print', list(
          extend = 'collection',
          buttons = c('csv', 'excel', 'pdf'),
          text = 'Download')
      ))
  )
```

