---
title: "Total Cases to Date"
author:
- name: Nicole Harty, MPH
  affiliation: Epidemiologist/Data Manager
date: "`r format(Sys.time(), '%B %d, %Y, %I %p')`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 5
    css: template.css
---

## Most Recent Week and Most Recent Two Weeks 
The following numbers reflect the most recent week and two week period through two days ago.   
  
Most Recent Week: **`r (as.Date(params$DataThroughDate)-days(6)) %>% format('%B %d, %Y')` through `r (as.Date(params$DataThroughDate)) %>% format('%B %d, %Y')`**.  
Most Recent Two Weeks: **`r (as.Date(params$DataThroughDate)-days(13)) %>% format('%B %d, %Y')` through `r as.Date(params$DataThroughDate) %>% format('%B %d, %Y')`**.  

```{r label=InternalTrackingNumbers}
InternalCurrentWeekRolling <- PHtracking %>%  
  filter(IsMostRecentWeekRolling=="Yes", `Resident or No`=="Resident") %>% 
  count() %>%
  pull()

InternalCurrent2WeekRolling <- PHtracking %>%  
  filter(IsMostRecent2WeeksRolling=="Yes", `Resident or No`=="Resident") %>% 
  count() %>%
  pull()

ResidentCases <- PHtracking %>% 
  filter(`Resident or No`=="Resident")

```


|Metric|Most Recent Week|Most Recent Two Weeks|
|-----|------|-----|
|New Cases|`r ConfProbCases %>% filter(IsMostRecentWeekRolling=="Yes") %>% count()`|`r ConfProbCases %>% filter(IsMostRecent2WeeksRolling=="Yes") %>% count()`|  
|Cases Per 100,000 People|`r ConfProbCases %>% filter(IsMostRecentWeekRolling=="Yes") %>% count() %>% mutate(CasesPer100K = round((n/params$RouttPop)*100000,1)) %>% pull(CasesPer100K)`|`r ConfProbCases %>% filter(IsMostRecent2WeeksRolling=="Yes") %>% count() %>% mutate(CasesPer100K = round((n/params$RouttPop)*100000,1)) %>% pull(CasesPer100K)`|  
|Total Tests Administered|`r DeDupNonAntibodyTests %>% ungroup() %>% filter(IsMostRecentWeekRolling=="Yes") %>% count()`|`r DeDupNonAntibodyTests %>% ungroup() %>% filter(IsMostRecent2WeeksRolling=="Yes") %>% count()`|  
|Total Visitor Cases|`r VisitorCases %>%  filter(IsMostRecentWeekRolling=="Yes") %>% count()`|`r VisitorCases %>%  filter(IsMostRecent2WeeksRolling=="Yes") %>% count()`|
|New Resident Cases, Routt County Public Health Internal Tracking|`r ResidentCases %>% filter(IsMostRecentWeekRolling=="Yes") %>% count()`|`r ResidentCases %>% filter(IsMostRecent2WeeksRolling=="Yes") %>% count()`|
|Routt County Resident COVID-19 Hospitalizations|`r COPHS %>% filter(IsMostRecentWeekRolling=="Yes") %>% summarise(Count = n_distinct(PersonID)) %>% mutate(HospitCountCat = case_when(Count==0 ~ "0",Count<5 ~ "1-4",Count<10 ~ "5-9",Count>10 ~ "10+")) %>% pull(HospitCountCat)`|`r COPHS %>% filter(IsMostRecent2WeeksRolling=="Yes") %>% summarise(Count = n_distinct(PersonID)) %>% mutate(HospitCountCat = case_when(Count==0 ~ "0",Count<5 ~ "1-4",Count<10 ~ "5-9",Count>10 ~ "10+")) %>% pull(HospitCountCat)`|
|COVID-19 Hospitalizations at Yampa Valley Medical Center|`r Hospit %>% filter(Hospital.Name=="Yampa Valley Medical Center"&IsMostRecentWeekRolling=="Yes") %>% summarise(Count = n()) %>% mutate(HospitCountCat = case_when(Count==0 ~ "0", Count<5 ~ "1-4", Count<10 ~ "5-9", Count>10 ~ "10+")) %>% pull(HospitCountCat)`|`r Hospit %>% filter(Hospital.Name=="Yampa Valley Medical Center"&IsMostRecent2WeeksRolling=="Yes") %>% summarise(Count = n()) %>% mutate(HospitCountCat = case_when(Count==0 ~ "0",Count<5 ~ "1-4",Count<10 ~ "5-9",Count>10 ~ "10+")) %>% pull(HospitCountCat)`|  
  
Hospitalizations are presented as a range to protect the identity of cases. Zero hospitalizations will be shown as such.

```{r label=CurrentWeekNumbers, eval = FALSE}
#This code chunk is for testing the code that is used inline above to produce number of incident cases in the current week,
#cases per 100K people and total tests administered
ConfProbCases %>%
  filter(AttributionWeekStart==params$MostRecentWeekStart) %>%
  count()

ConfProbCases %>%
  filter(CollectionWeekStart==params$MostRecentWeekStart) %>%
  count() %>%
  mutate(CasesPer100K = round((n/params$RouttPop)*100000,1)) %>%
  pull(CasesPer100K)


#use this to check cases
ConfProbCases %>%
  select(eventid, last_name, first_name, reporteddate, AttributionDate, CollectionDateWeek, earliest_collectiondate) %>%
  arrange(CollectionDateWeek, earliest_collectiondate, AttributionDate)


COPHS %>%
  filter(IsMostRecentWeekRolling=="Yes") %>%
  summarise(Count = n_distinct(PersonID)) %>%
  pull(Count)
  
```
```{r label=TwoCurrentWeekNumbers, eval = FALSE}
#This code chunk is for testing the code that is used inline above to produce number of incident cases in the current week,
#cases per 100K people and total tests administered
ConfProbCases %>%
  filter(IsMostRecent2Weeks=="Yes") %>%
  select(eventid, last_name, first_name, reporteddate, AttributionDate, casestatus) %>%
  group_by(AttributionDate) %>%
  count()

ConfProbCases %>%
  filter(IsMostRecent2Weeks=="Yes") %>%
  count() %>%
  mutate(CasesPer100K = round((n/params$RouttPop)*100000,1))

#Below is the 2week incidence using report date, that the state does
ConfProbCases %>%
  filter(reporteddate>="2020-09-14"&reporteddate<"2020-09-28") %>%
  count() %>%
  mutate(CasesPer100K = round((n/params$RouttPop)*100000,1))


#Data quality checks
ConfProbCases %>%
  filter(casestatus=="Probable") %>%
  select(eventid, last_name, first_name, reporteddate, AttributionDate)

ConfProbCases %>%
  filter(casestatus=="Confirmed") %>%
  select(eventid, last_name, first_name, reporteddate, AttributionDate, gender) %>%
  group_by(AttributionDate, gender) %>%
  arrange(AttributionDate)
```

