---
title: "Positivity"
author:
- name: Nicole Harty, MPH
  affiliation: Epidemiologist/Data Manager
date: "`r format(Sys.time(), '%B %d, %Y, %I %p')`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 5
    css: template.css
---

## Positivity  

```{r label=PositivityComparisonPREP}
PCRpositivity <- ConfProbCases %>%
  filter(casestatus=="confirmed") %>%
  group_by(AttributionDate) %>%
  summarise(Cases = n()) %>%
  full_join(NonAntibodyTests %>%
              filter(test_type=="PCR") %>%
              group_by(collectiondate) %>%
              summarise(TotalTests = n()),
            by = c("AttributionDate" = "collectiondate")) %>%
  #  replace(., is.na(.), 0) %>%
  right_join((Calendar %>%
                select(date) %>%
                filter(date>"2020-02-29"&date<=(params$DataThroughDate))), by = c("AttributionDate" = "date")) %>%
  replace(., is.na(.), 0) %>%
  arrange(AttributionDate) %>%
  mutate(Sum14DayCases = zoo::rollsumr(Cases, k=14, fill=NA, na.rm=TRUE),
         Sum14DayTests = zoo::rollsumr(TotalTests, k=14, fill = NA, na.rm=TRUE),
         Rolling14DayPositivityPCR = (Sum14DayCases/Sum14DayTests)*100)

ANITGENpositivity <- ConfProbCases %>%
  filter(casestatus=="probable", !is.na(collectiondate)) %>%
  group_by(AttributionDate) %>%
  summarise(Cases = n()) %>%
  full_join(NonAntibodyTests %>%
              filter(test_type=="antigen") %>%
              group_by(collectiondate) %>%
              summarise(TotalTests = n()),
            by = c("AttributionDate" = "collectiondate")) %>%
  #  replace(., is.na(.), 0) %>%
  right_join((Calendar %>%
                select(date) %>%
                filter(date>"2020-02-29"&date<=(params$DataThroughDate))), by = c("AttributionDate" = "date")) %>%
  replace(., is.na(.), 0) %>%
  arrange(AttributionDate) %>%
  mutate(Sum14DayCases = zoo::rollsumr(Cases, k=14, fill=NA, na.rm=TRUE),
         Sum14DayTests = zoo::rollsumr(TotalTests, k=14, fill = NA, na.rm=TRUE),
         Rolling14DayPositivityANTIGEN = (Sum14DayCases/Sum14DayTests)*100)

POStxtTable <- ConfProbCases %>%
  filter(!is.na(collectiondate)) %>%
  group_by(AttributionDate) %>%
  summarise(Cases = n()) %>%
  full_join(DeDupNonAntibodyTests %>%
              group_by(collectiondate) %>%
              summarise(TotalTests = n()),
            by = c("AttributionDate" = "collectiondate")) %>%
  #  replace(., is.na(.), 0) %>%
  right_join((Calendar %>%
                select(date) %>%
                filter(date>"2020-02-29"&date<=(params$DataThroughDate))), by = c("AttributionDate" = "date")) %>%
  replace(., is.na(.), 0) %>%
  arrange(AttributionDate) %>%
  mutate(Sum14DayCases = zoo::rollsumr(Cases, k=14, fill=NA, na.rm=TRUE),
         Sum14DayTests = zoo::rollsumr(TotalTests, k=14, fill = NA, na.rm=TRUE),
         Rolling14DayPositivity = (Sum14DayCases/Sum14DayTests)*100)

ADULTpositivity <- ConfProbCases %>%
  filter(!is.na(collectiondate),age_at_reported>17) %>%
  group_by(AttributionDate) %>%
  summarise(Cases = n()) %>%
  full_join(NonAntibodyTests %>%
              filter(age>17) %>%
              group_by(collectiondate) %>%
              summarise(TotalTests = n()),
            by = c("AttributionDate" = "collectiondate")) %>%
  #  replace(., is.na(.), 0) %>%
  right_join((Calendar %>%
                select(date) %>%
                filter(date>"2020-02-29"&date<=(params$DataThroughDate))), by = c("AttributionDate" = "date")) %>%
  replace(., is.na(.), 0) %>%
  arrange(AttributionDate) %>%
  mutate(Sum14DayCases = zoo::rollsumr(Cases, k=14, fill=NA, na.rm=TRUE),
         Sum14DayTests = zoo::rollsumr(TotalTests, k=14, fill = NA, na.rm=TRUE),
         Rolling14DayPositivityADULTS = (Sum14DayCases/Sum14DayTests)*100)

CHILDpositivity <- ConfProbCases %>%
  filter(!is.na(collectiondate),age_at_reported<18) %>%
  group_by(AttributionDate) %>%
  summarise(Cases = n()) %>%
  full_join(NonAntibodyTests %>%
              filter(age<18) %>%
              group_by(collectiondate) %>%
              summarise(TotalTests = n()),
            by = c("AttributionDate" = "collectiondate")) %>%
  #  replace(., is.na(.), 0) %>%
  right_join((Calendar %>%
                select(date) %>%
                filter(date>"2020-02-29"&date<=(params$DataThroughDate))), by = c("AttributionDate" = "date")) %>%
  replace(., is.na(.), 0) %>%
  arrange(AttributionDate) %>%
  mutate(Sum14DayCases = zoo::rollsumr(Cases, k=14, fill=NA, na.rm=TRUE),
         Sum14DayTests = zoo::rollsumr(TotalTests, k=14, fill = NA, na.rm=TRUE),
         Rolling14DayPositivityCHILDREN = (Sum14DayCases/Sum14DayTests)*100)
```

The graph below compares test positivity among all tests (PCR and non-home test antigen) to that of PCR tests and antigen tests alone. Comparing positivity among antigen tests and PCR tests is important because schools in the Steamboat Springs area began their weekly surveillance testing program that uses antigen tests in early October. The implementation of this program impacted the test positivity resulting in the overall Routt County test positivity calculated using both antigen and PCR tests no longer aligning closely with the calculation CDPHE has with just PCR tests.  

```{r label=PositivityComparisonTestType}
PCRpositivity %>%
  select(AttributionDate, Rolling14DayPositivityPCR) %>%
  left_join(ANITGENpositivity %>% 
              select(AttributionDate, Rolling14DayPositivityANTIGEN), by = "AttributionDate") %>%
  filter(AttributionDate>="2020-10-05") %>%
  plot_ly(x = ~AttributionDate,
          y = ~Rolling14DayPositivityPCR,
          type = "scatter",
          color = I("#4E2B1F"),
          mode = "lines",
          yaxis = "y",
          name = "PCR Positivity") %>%
  add_trace(x = ~AttributionDate,
            y = ~Rolling14DayPositivityANTIGEN,
            type = "scatter",
            name = "Antigen Positiviity",
            mode = "lines",
            color = I("#BB4628")) %>%
  add_trace(data = POStxtTable %>%
              filter(AttributionDate>="2020-10-05"),
            x = ~AttributionDate,
            y = ~Rolling14DayPositivity,
            type = "scatter",
            name = "Overall Positiviity",
            mode = "lines",
            color = I("#F2BF4C")) %>%
  layout(margin = list(l=50,r=50,b=155,h=175),
         title = "Rolling 14-day Positivity by Test Type Compared to County Total",
         xaxis = list(type = 'date',
                      tickformat = "%b %d, %Y",
                      autotick = F, 
                      tickangle = 45,
                      tick0 = "2000-01-10",
                      dtick = 1814400000,
                      title = "Week Start (all dates are Mondays)",
                      showgrid = FALSE),
         yaxis = list(title = "Positivity Rate (%)"),
         legend = list(orientation = 'h', y=-.3),
         font = list(family = "Arial", size = 12),
                annotations = list(
           list(x = .0,
                y = .5,
                text = "Data prepared by Routt County Public Health",
                xref = "paper",
                yref = 'paper',
                showarrow = FALSE,
                font = list(family = "Arial", size = 12, color = "gray"))
            )
         )

```

```{r label=PositivityComparisonAgeGroup, eval = params$Internal}
ADULTpositivity %>%
  select(AttributionDate, Rolling14DayPositivityADULTS) %>%
  left_join(CHILDpositivity %>%
              select(AttributionDate, Rolling14DayPositivityCHILDREN), by = "AttributionDate") %>%
  filter(AttributionDate>="2020-09-21") %>%
  plot_ly(x = ~AttributionDate,
          y = ~Rolling14DayPositivityADULTS,
          type = "scatter",
          color = I("#4E2B1F"),
          mode = "lines",
          yaxis = "y",
          name = "ADULT Positivity (18+)") %>%
  add_trace(x = ~AttributionDate,
            y = ~Rolling14DayPositivityCHILDREN,
            type = "scatter",
            name = "CHILD Positiviity (<18)",
            mode = "lines",
            color = I("#BB4628")) %>%
  add_trace(data = POStxtTable %>%
              filter(AttributionDate>="2020-09-21"),
            x = ~AttributionDate,
            y = ~Rolling14DayPositivity,
            type = "scatter",
            name = "Overall Positiviity",
            mode = "lines",
            color = I("#F2BF4C")) %>%
  layout(margin = list(l=50,r=50,b=155,h=175),
         title = "Rolling 14-day Positivity by Age Group Compared to County Total",
         xaxis = list(type = 'date',
                      tickformat = "%b %d, %Y",
                      autotick = F,
                      tickangle = 45,
                      tick0 = "2000-01-10",
                      dtick = 1814400000,
                      title = "Week Start (all dates are Mondays)",
                      showgrid = FALSE),
         yaxis = list(title = "Positivity Rate (%)"),
         legend = list(orientation = 'h', y=-.3),
         font = list(family = "Arial", size = 12),
                annotations = list(
           list(x = .0,
                y = .5,
                text = "Data prepared by Routt County Public Health",
                xref = "paper",
                yref = 'paper',
                showarrow = FALSE,
                font = list(family = "Arial", size = 12, color = "gray"))
            )
         )

```

```{r label=TestVolumeCompare, eval=params$Internal}
PCRpositivity %>%
  select(AttributionDate, Sum14DayTestsPCR = Sum14DayTests) %>%
  left_join(ANITGENpositivity %>% 
              select(AttributionDate, Sum14DayTestsANTIGEN = Sum14DayTests), by = "AttributionDate") %>%
  filter(AttributionDate>="2020-10-05") %>%
  left_join(POStxtTable %>%
              select(AttributionDate, Sum14DayTests) %>%
              filter(AttributionDate>="2020-10-05")) %>%
  mutate(PropANTIGEN = Sum14DayTestsANTIGEN/Sum14DayTests,
         PropPCR = Sum14DayTestsPCR/Sum14DayTests) %>%
  plot_ly(x = ~AttributionDate,
          y = ~Sum14DayTestsPCR,
          type = "scatter",
          fillcolor = I("#4E2B1F"),
          mode = "none",
          stackgroup = "one",
          groupnorm = 'percent',
          yaxis = "y",
          name = "14-day PCR Test Percentage") %>%
  add_trace(x = ~AttributionDate,
            y = ~Sum14DayTestsANTIGEN,
            type = "scatter",
            name = "14-day Antigen Test Percentage",
            fillcolor = I("#BB4628")) %>%
  layout(margin = list(l=50,r=50,b=155,h=175),
         title = "Rolling 14-day Proportion of Tests by Test Type",
         xaxis = list(type = 'date',
                      tickformat = "%b %d, %Y",
                      autotick = F, 
                      tickangle = 45,
                      tick0 = "2000-01-10",
                      dtick = 1814400000,
                      title = "Week Start (all dates are Mondays)",
                      showgrid = FALSE),
         yaxis = list(title = "Proportion"),
         legend = list(orientation = 'h', y=-.3),
         font = list(family = "Arial", size = 12),
          annotations = list(
           list(x = .0,
                y = .5,
                text = "Data prepared by Routt County Public Health",
                xref = "paper",
                yref = 'paper',
                showarrow = FALSE,
                font = list(family = "Arial", size = 12, color = "gray"))
            )
         )

```

```{r label=Rolling14PositivityTestVolumeTestType, eval=params$Internal}

plot_ly(data = (PCRpositivity %>%
                  select(AttributionDate, Sum14DayTestsPCR = Sum14DayTests) %>%
                  mutate(Sum14DayPCRtestsDaily = Sum14DayTestsPCR/14)),
          x = ~AttributionDate,
          y = ~Sum14DayPCRtestsDaily,
          type = "bar",
          color = I("#BB4628"),
          # mode = "none",
          # stackgroup = "one",
          # groupnorm = 'percent',
          yaxis = "y",
          name = "14-day PCR Test Daily Rate") %>%
  add_trace(data = (ANITGENpositivity %>%
                      select(AttributionDate, Sum14DayTestsANTIGEN = Sum14DayTests) %>%
                      mutate(Sum14DayANTIGENtestsDaily = Sum14DayTestsANTIGEN/14)),
            x = ~AttributionDate,
            y = ~Sum14DayANTIGENtestsDaily,
            type = "bar",
            yaxis = "y",
            name = "14-day Antigen Test Raily Rate",
            color = I("#F2BF4C")) %>%
add_trace(data = (ConfProbCases %>%
                    group_by(AttributionDate) %>%
                    summarise(Cases = n()) %>%
                    full_join(DeDupNonAntibodyTests %>%
                                group_by(collectiondate) %>%
                                summarise(TotalTests = n()),
                              by = c("AttributionDate" = "collectiondate")) %>%
                    #  replace(., is.na(.), 0) %>%
                    right_join((Calendar %>%
                                  select(date) %>%
                                  filter(date>"2020-02-29"&date<=(params$DataThroughDate))), by = c("AttributionDate" = "date")) %>%
                    replace(., is.na(.), 0) %>%
                    arrange(AttributionDate) %>%
                    mutate(Sum14DayCases = zoo::rollsumr(Cases, k=14, fill=NA, na.rm=TRUE),
                           Sum14DayTests = zoo::rollsumr(TotalTests, k=14, fill = NA, na.rm=TRUE),
                           Rolling14DayPositivity = (Sum14DayCases/Sum14DayTests)*100)# %>%
                  #  filter(AttributionDate>="2020-10-05")
                          ),
          x = ~AttributionDate,
          y = ~Rolling14DayPositivity,
          type = "scatter",
          name = "Rolling 14-day Positivity Rate",
          yaxis = "y2",
          mode = "lines",
          color = I("#4E2B1F")) %>%
  layout(margin = list(l=50,r=50,b=155,h=175),
         title = "Rolling 14-day Positivity with Antigen and PCR Test Volume",
         xaxis = list(type = 'date',
                      tickformat = "%b %d, %Y",
                      autotick = F, 
                      tickangle = 45,
                      tick0 = "2000-01-10",
                      dtick = 1814400000,
                      title = "Week Start (all dates are Mondays)"),
         yaxis = list(title = "Test Volume"),
         legend = list(orientation = 'h', y=-.3),
         font = list(family = "Arial", size = 12),
         barmode = "stack",
         yaxis2 = list(
           tickfont = list(color = "#4E2B1F"),
           overlaying = "y",
           side = "right",
           title = "Positivity",
           rangemode = "tozero",
           showgrid = FALSE)
         )
``` 
