---
title: "Surveillance - Vaccine Efficacy"
author:
- name: Nicole Harty, MPH
  affiliation: Epidemiologist/Data Manager
date: "`r format(Sys.time(), '%B %d, %Y, %I %p')`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 5
    css: template.css
---

## Vaccine Efficacy and Breakthrough Cases  
Clinical trials for COVID-19 vaccines were designed to assess efficacy in preventing severe disease, hospitalization, and/or death. No vaccine is 100% effective. Therefore, we expect to see vaccine breakthrough cases, and we expect to see a small proportion of cases (5-15%) among vaccinated individuals who do develop severe disease, hospitalization, or death. 
Vaccine breakthrough is defined as a positive COVID-19 test at least 14 days after completing the COVID-19 vaccination series. Identifying vaccine breakthrough relies upon data in CIIS as well as self-reported (and later verified) information gathered during case investigations.  
 

```{r label=VaxBreakthroughbyMonthGraph3, eval = params$Internal}
FullyVax %>%
  filter(FullyVaxDateAttr>"2021-01-31") %>%
  select(patient_id, FullyVaxDateAttr) %>%
  distinct() %>%
  group_by(FullyVaxDateAttr) %>%
  summarise(Count = n()) %>%
  mutate(RollingSumFullyVax = cumsum(Count),
         FullyVaxPercent = round((RollingSumFullyVax/params$RouttPop)*100,2),
         NotFullyVaxPercent = round(((params$RouttPop-RollingSumFullyVax)/params$RouttPop)*100,2)) %>%
  left_join(ConfProbCases %>%
              filter(breakthrough==TRUE,AttributionDate>"2021-01-31") %>%
              group_by(AttributionDateMonthStart) %>%
              summarise(VaxBreakthrough = n()) %>%
              left_join(ConfProbCases %>%
                          mutate(AttributionMonth = as.Date(paste0(year(AttributionDate),"-",month(AttributionDate),"-01"))) %>%
                          filter(age_at_reported>11, AttributionMonth>"2021-01-31") %>%
                          group_by(AttributionMonth) %>%
                          summarise(Total = n()), by = c("AttributionDateMonthStart" = "AttributionMonth")) %>%
              mutate(VaxBreakthroughPercent = round((VaxBreakthrough/Total)*100,2)), by = c("FullyVaxDateAttr" = "AttributionDateMonthStart")) %>%
  filter(FullyVaxDateAttr<=as.Date(paste0(year(Sys.Date()),"-",(month(Sys.Date())),"-01"))) %>%
  plot_ly(
    x = ~FullyVaxDateAttr,
    y = ~FullyVaxPercent,
    type = "bar",
    name = "Fully Vaccinated",
    color = I("#4E2B1F")) %>%
  add_trace(y = ~NotFullyVaxPercent,
            type = "bar",
            name = 'Not Fully Vaccinated',
            color = I("#BB4628")) %>%
  add_trace(y = ~VaxBreakthroughPercent,
            type = "scatter",
            mode = "line",
            line = list(color = '#F2BF4C'),
            name = 'Monthly Proportion Vaccine Breakthrough',
            yaxis = "y2") %>%
  layout(margin = list(l=50,r=50,h=100),
         title = "Monthly Fully Vaccinated (brown bar) and Proportion Monthly<br>Vaccine Breakthrough Cases (line)",
         xaxis = list(title ="Month"),
         yaxis = list(title = "Percentage of Cases",
                      rangemode = "tozero"),
         yaxis2 = list(
           tickfont = list(color = "#4E2B1F"),
           overlaying = "y",
           side = "right",
           title = "Monthly Proportion of Vaccine Breakthrough Cases",
           rangemode = "tozero",
           range = c(0,100),
           showgrid = F),
         barmode = "stack",
         font = list(family = "Arial", size = 12),
         legend = list(orientation = 'h', y=-.25))


```

```{r label=VaxBreakthroughbyMonthGraph4}

#Need to add 5-11 year olds into case denom beginning January 2022

FullyVax %>%
 filter(FullyVaxDateAttr>"2021-01-31") %>%
  group_by(FullyVaxDateAttr) %>%
  summarise(Count = n()) %>%
  mutate(RollingSumFullyVax = cumsum(Count),
         FullyVaxPercent = round((RollingSumFullyVax/params$RouttPop)*100,2),
         NotFullyVaxPercent = round(((params$RouttPop-RollingSumFullyVax)/params$RouttPop)*100,2)) %>%
  left_join(ConfProbCases %>%
             filter(breakthrough==TRUE,AttributionDate>"2021-01-31") %>%
              group_by(AttributionDateMonthStart) %>%
              summarise(VaxBreakthrough = n()) %>%
              left_join(ConfProbCases %>%
                          mutate(AttributionMonth = as.Date(paste0(year(AttributionDate),"-",month(AttributionDate),"-01"))) %>%
                         filter(age_at_reported>11, AttributionDate>"2021-01-31") %>%
                          group_by(AttributionMonth) %>%
                          summarise(Total = n()), by = c("AttributionDateMonthStart" = "AttributionMonth")) %>%
              mutate(VaxBreakthroughPercent = round((VaxBreakthrough/Total)*100,2)), by = c("FullyVaxDateAttr" = "AttributionDateMonthStart")) %>%
  filter(FullyVaxDateAttr<as.Date(paste0(year(Sys.Date()),"-",(month(Sys.Date())),"-01"))) %>%
plot_ly(
  x = ~FullyVaxDateAttr,
  y = ~FullyVaxPercent,
            type = "bar",
            name = "Monthly Percentage Population Fully Vaccinated: <br># Routt County residents more than 14 days <br>beyond final dose divided by total population",
            color = I("#4E2B1F")) %>%
  add_trace(y = ~VaxBreakthroughPercent,
            type = "bar",
            color = I('#BB4628'),
            name = 'Monthly Percentage Vaccine Breakthrough Cases: <br># vaccine breakthrough cases divided <br>by total # cases age 12+') %>%
  layout(margin(b=500),
         title = list(text = "Percentage Population Fully Vaccinated (brown) and <br>Percentage of Vaccine Breakthrough Cases Ages 12+ (orange), by Month"),
         xaxis = list(title ="Month"),
         yaxis = list(title = "Percentage",
                    range = c(0,100)),
         barmode = "group",
         font = list(family = "Arial", size = 12),
        legend = list(orientation = 'h', y=-.25))
```

```{r label=VaxEfficacyCDPHE_pointINtime}
# **POINT IN TIME ANALYSIS BROKE WITH UPDATE TO CEDRS EXPORT FOR BREAKTHROUGH**
# source("point_in_time_ve.R")
# 
# efficacy %>% 
#   mutate(efficacy = round(efficacy*100,2)) %>%
#   filter(week>="2021-02-01") %>%
#   left_join((ConfProbCases %>%
#               group_by(AttributionWeekStart) %>%
#               summarise(NumberCases = n()) %>%
#               right_join((Calendar %>%
#                             select(WeekStart) %>%
#                             distinct()), by = c("AttributionWeekStart" = "WeekStart")) %>%
#               replace(., is.na(.), 0) %>%
#               arrange(AttributionWeekStart) %>%
#               filter(AttributionWeekStart<=params$MostRecentWeekStart&AttributionWeekStart>"2020-02-21") %>%
#               mutate(TwoWeekCases=zoo::rollsumr(NumberCases, k = 2, fill = NA),
#                      TwoWeekRate=(TwoWeekCases/25652*100000)) %>%
#               mutate(TwoWeekStartDate = AttributionWeekStart-7,
#                      TwoWeekEndDate = AttributionWeekStart+6)), by = c("week" = "AttributionWeekStart")) %>%
#   plot_ly(x = ~week,
#          y = ~efficacy,
#          type = "scatter",
#          mode = "lines",
#          color = I("#4E2B1F"),
#          name = "Vaccine Efficacy") %>%
#   add_trace(x = ~week,
#             y = ~TwoWeekCases,
#             type = "scatter",
#             name = "Two Week (14 day) Case Count",
#             color = I("#BB4628"),
#             mode = "lines",
#             yaxis = "y2") %>%
#   layout(margin = list(l=50,r=50,h=100),
#          title = list(text = "Point in Time Vaccine Efficacy by Week as Compared to Case Counts"),
#          xaxis = list(title ="Week Start"),
#          yaxis = list(title = "Vaccine Efficacy",
#                     range = c(0,100)),
#          yaxis2 = list(title = "Weekly Sum Cases",
#                        side = "right",
#                        overlaying = "y",
#                        rangemode = "tozero",
#                        showgrid = F),
#          font = list(family = "Arial", size = 12),
#          legend = list(orientation = 'h', y=-.25))

```

```{r label=VaxBreakthroughDemos, eval = params$Internal}
ConfProbCases%>%
  filter(breakthrough==TRUE) %>%
  group_by(gender) %>%
  count() %>%
  kable(caption = "Gender Breakdown of Vaccine Breakthrough Cases")

ConfProbCases%>%
  filter(breakthrough==TRUE) %>%
  group_by(AgeGrouping) %>%
  count() %>%
  mutate(Percentage = scales::percent(n/(VaxBreakthroughList %>% count() %>% pull()))) %>%
  kable(caption = "Age Breakdown of Vaccine Breakthrough Cases")

ConfProbCases%>%
  filter(breakthrough==TRUE) %>%
  group_by(outbreak_transmission_type) %>%
  count() %>%
  kable(caption = "Source of Exposure of Vaccine Breakthrough Cases")

ConfProbCases%>%
  filter(breakthrough==TRUE) %>%
  group_by(outbreakyesno) %>%
  count() %>%
  kable(caption = "Outbreak Connection for Vaccine Breakthrough Cases")


```

```{r label=VaxBreakthroughDuration, eval = params$Internal}
Histogram <- ConfProbCases %>%
  filter(breakthrough==TRUE) %>%
  mutate(DaysBtwn = as.numeric(AttributionDate)-as.numeric(vax_utd14)) %>%
  select(eventid, DaysBtwn) %>%
  filter(DaysBtwn>0) %>%
  mutate(MonthsBtwn = DaysBtwn/30.5)
hist(Histogram$DaysBtwn,
     xlab = "Days Between 2nd Dose and Positive Test",
     main = "Days Between 2nd Dose and Positive Test of Breakthrough Cases")

hist(Histogram$MonthsBtwn,
     xlab = "Months Between 2nd Dose and Positive Test",
     main = "Months Between 2nd Dose and Positive Test of Breakthrough Cases")

Hist65plus <- ConfProbCases %>%
  filter(breakthrough==TRUE, age_at_reported>64) %>%
  mutate(DaysBtwn = as.numeric(AttributionDate)-as.numeric(vax_utd14)) %>%
  select(eventid, DaysBtwn) %>%
  filter(DaysBtwn>0) %>%
  mutate(MonthsBtwn = DaysBtwn/30.5)

hist(Hist65plus$MonthsBtwn,
     xlab = "Months Between 2nd Dose and Positive Test, Age 65+",
     main = "Months Between 2nd Dose and Positive Test, Age 65+ Breakthrough Cases")
```

```{r label=VaxBreaktrhoughDOSES, eval = params$Internal}
DoseInfoVaxBreakthrough %>%
  group_by(vaccination_code) %>%
  count() %>%
  left_join(PtIZ %>%
              group_by(vaccination_code) %>%
              summarise(Total = n()), by = "vaccination_code") %>%
  mutate("Percent of Doses"= (n/Total)*100) %>%
  kable(caption = "Doses Associated with Vaccine Breakthrough by Manufacturer")

DoseInfoVaxBreakthrough %>%
  group_by(clinic_desc) %>%
  count() %>%
  left_join(PtIZ %>%
              group_by(clinic_desc) %>%
              summarise(Total = n()), by = "clinic_desc") %>%
  mutate("Percent of Doses"= (n/Total)*100) %>%
  kable(caption = "Doses Associated with Vaccine Breakthrough by Clinic")
```

```{asis, echo=params$Internal}
## Booster Doses
 
```


```{r label=BoosterDoses, eval = params$Internal}
PtIZ %>%
  filter(vaccination_code=="COVID-19 Vector-NR (JSN)") %>%
  select(patient_id) %>%
  distinct() %>%
  left_join(PtIZ %>%
              select(patient_id, vaccination_code, dosage_num, vaccination_date), by = "patient_id") %>%
  filter(vaccination_code!="COVID-19 Vector-NR (JSN)") %>%
  count() %>%
  kable(caption = "Number of people who received J&J and then another manufacturer dose")

PtIZ %>%
  filter(age_at_1stvaccination>=65) %>%
  select(patient_id) %>%
  distinct() %>%
  left_join(PtIZ %>%
              select(patient_id, vaccination_code, dosage_num, vaccination_date), by = "patient_id") %>%
  group_by(vaccination_code, dosage_num) %>%
  summarise(Count = n_distinct(patient_id)) %>%
  kable(caption = "Count of Dosage Number of Each Manufacturer for those >65 years")

PtIZ %>%
  filter(dosage_num==3) %>%
  select(patient_id) %>%
  left_join(PtIZ, by = "patient_id") %>%
  group_by(dosage_num) %>%
  count() %>%
  kable(caption = "Number of each Dosage Reported") 
  
PtIZ %>%
  filter(vaccination_code=="COVID-19 mRNA (MOD)") %>%
  select(patient_id) %>%
  distinct() %>%
  left_join(PtIZ %>%
              select(patient_id, vaccination_code, dosage_num, vaccination_date), by = "patient_id") %>%
  filter(vaccination_code!="COVID-19 mRNA (MOD)") %>%
  count() %>%
  kable(caption = "Number of people who received Moderna and then another manufacturer dose")

PtIZ %>%
  filter(vaccination_code=="COVID-19 mRNA (PFR)") %>%
  select(patient_id) %>%
  distinct() %>%
  left_join(PtIZ %>%
              select(patient_id, vaccination_code, dosage_num, vaccination_date), by = "patient_id") %>%
  filter(vaccination_code!="COVID-19 mRNA (PFR)") %>%
  count() %>%
  kable(caption = "Number of people who received Pfizer and then another manufacturer dose")

  
```

```{r label=BoosterDemos, eval = params$Internal}
RouttPopTable2$AgeGroup10yr <- fct_recode(RouttPopTable2$AgeGroup10yr, "90 and over" = "90-99")
PtIZ %>%
  filter(dosage_num==3) %>%
  select(patient_id, AgeGroup10yr) %>%
  distinct() %>%
  group_by(AgeGroup10yr) %>%
  count() %>%
  left_join(RouttPopTable2 %>%
              select(AgeGroup10yr, TOTAL) %>%
              group_by(AgeGroup10yr) %>%
              summarise(POPTotal=sum(TOTAL)), by = "AgeGroup10yr") %>%
  mutate(PercentPop = scales::percent(n/POPTotal)) %>%
  kable(caption = "Booster Recipients by Decade of Age")

PtIZ %>%
  filter(dosage_num==3) %>%
  group_by(gender_code) %>%
  count() %>%
  kable(caption = "Gender Breakdown of Booster Recipients")

PtIZ %>%
  filter(dosage_num==3) %>%
  group_by(City) %>%
  count() %>%
  left_join(RouttPopGeog,
             by = c("City")) %>%
  mutate(PropBooster = scales::percent(n/(PtIZ %>%
                                            filter(dosage_num==3) %>%
                                            count()) %>%
                                         pull(n)),
         PropPop = scales::percent(Pop/RouttPopGeog %>%
                                        summarise(POPtotal=sum(Pop)) %>%
                                     pull(POPtotal))) %>%
  kable(caption = "Region Breakdown of Booster Recipients")



```

```{r label=BoosterDosesUptake, eval = params$Internal}
# PtIZ %>%
#   filter(dosage_num==3) %>%
#   select(patient_id, AgeGroup10yr, vaccination_date, vaccination_code, DoseDateWeekStart) %>%
#   distinct() %>%
#   group_by(DoseDateWeekStart) %>%
#   summarise(AllAgesBoosters = n()) %>%
#   ungroup() %>%
#   mutate(AllAgesRunningSum = cumsum(AllAgesBoosters)) %>%
#   left_join(PtIZ %>%
#               filter(dosage_num==3) %>%
#               select(patient_id, AgeGroup10yr, vaccination_date, vaccination_code, DoseDateWeekStart) %>%
#               distinct() %>%
#               group_by(DoseDateWeekStart, AgeGroup10yr) %>%
#               count())


BoosterDosesOverTime <- PtIZ %>%
  filter(dosage_num==3) %>%
  select(patient_id, age_at_1stvaccination, vaccination_date, vaccination_code, DoseDateWeekStart) %>%
  distinct() %>%
  mutate(AgeCategory = case_when(age_at_1stvaccination>=65 ~ "65+",
                                 age_at_1stvaccination>=30~ "30-64",
                                 TRUE ~ "Under 30")) %>%
  group_by(DoseDateWeekStart, AgeCategory) %>%
  count() %>%
  right_join(Calendar %>%
              select(WeekStart) %>%
              distinct() %>%
              mutate(col1 = "Under 30", 
                     col2 = "30-64",
                     col3 = "65+") %>%
              pivot_longer(cols = 2:4) %>%
              select(1,3), by = c("DoseDateWeekStart" = "WeekStart", "AgeCategory" = "value")) %>%
  replace(., is.na(.), 0) %>%
  filter(DoseDateWeekStart>"2021-08-01"&DoseDateWeekStart<=params$DataThroughDate) %>%
  arrange(DoseDateWeekStart) 


BoosterDosesOverTime$AgeCategory <- as.factor(BoosterDosesOverTime$AgeCategory)
BoosterDosesOverTime$AgeCategory <- fct_relevel(BoosterDosesOverTime$AgeCategory, "Under 30", .before = "30-64")


plot_ly() %>%

add_trace(data = (ConfProbCases %>%
                    group_by(AttributionWeekStart) %>%
                    summarise(NumberCases = n()) %>%
                    right_join((Calendar %>%
                                  select(WeekStart) %>%
                                  distinct()), by = c("AttributionWeekStart" = "WeekStart")) %>%
                    replace(., is.na(.), 0) %>%
                    arrange(AttributionWeekStart) %>%
                    filter(AttributionWeekStart<=params$MostRecentWeekStart) %>%
                    mutate(TwoWeekCases=zoo::rollsumr(NumberCases, k = 2, fill = NA),
                           TwoWeekRate=(TwoWeekCases/25652*100000)) %>%
                    filter(AttributionWeekStart>"2021-08-01"&AttributionWeekStart<=params$MostRecentWeekStart)),
          x = ~AttributionWeekStart,
          y = ~TwoWeekRate,
          type = 'scatter',
          mode = 'lines',
          yaxis = "y2",
          name = '14-Day Incidence Rate per 100,000 Population',
          line = list(color = '#F2BF4C')
          ) %>%
  
  add_trace(data = BoosterDosesOverTime,
          x = ~DoseDateWeekStart,
        y = ~n,
        color = ~AgeCategory,
        colors = c('#4E2B1F', '#BB4628', "#477691"),
        type= "bar",
        legendgroup = ~AgeCategory
        ) %>%
  
  layout(barmode = 'stack',
         title ="Number of Booster Doses by Age Category Overlayed with Incidence Rate",
         xaxis = list(
           title = "Week Start",
           font = list (family = "Arial",size = 14),
           tickangle = -45,
           type = 'category'
           ),
         yaxis = list (
           title = "# People Received 3rd Dose",
           font = list (family = "Arial",size = 14)
           ),
         yaxis2 = list(
           overlaying = "y",
           side = "right",
           title = "14-Day Incidence Rate",
           rangemode = "tozero",
           showgrid = F)
         )
  
```


