---
title: "Case Outcomes"
author:
- name: Nicole Harty, MPH
  affiliation: Epidemiologist/Data Manager
date: "`r format(Sys.time(), '%B %d, %Y, %I %p')`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 5
    css: template.css
---

## Case Outcomes  
Case outcomes are reported according to the most severe outcome during the illness. For example, a hospitalized patient will be listed as hospitalized even after they have returned home. Outcome definitions are as follows:  
  
* Died = patient reported as died in CEDRS
* Hospitalized = hospitalized during illness
* Recovered = more than 28 days have passed since symptoms or test AND not hospitalized AND not died
* Active = within 28 days of symptoms or test

```{r label=CaseOutcomes}
ConfProbCases <- ConfProbCases %>%
  mutate(CaseOutcome = case_when(outcome=="Patient died" ~ "Died",
                                 hospitalized=="TRUE" ~ "Hospitalized",
                                 difftime(params$DataThroughDate,onsetdate_proxy_dist, units = "days")>28 ~ "Recovered",
                                 TRUE ~ as.character("Active"))) 

plot_ly() %>%
  add_pie(data = ConfProbCases %>%
            group_by(CaseOutcome) %>%
            count(),
          labels = ~CaseOutcome, values = ~n,
          marker = list(colors = c('#4E2B1F', '#BB4628', "#477691", "#F2BF4C"))) %>%
  layout(margin = c(t=150),
         title = list(text = "COVID-19 Case Outcomes",
                      yref = "paper",
                      y = 1.5,
                      font = list(family = "Arial", size = 14)))
```

```{r label=CaseOutcomesAge}

ConfProbCases %>%
  mutate(day = day(AttributionDate),
         month = month(AttributionDate),
         year = year(AttributionDate)) %>%
  filter(year(AttributionDate)<year(Sys.Date())|
         month(AttributionDate)<month(Sys.Date())
        |
        ((month(AttributionDate)==month(Sys.Date())&(day<30)))
         ) %>%
  group_by(age_group, CaseOutcome) %>%
  summarise(NumberCases = n()) %>%
  pivot_wider(names_from = CaseOutcome, values_from = NumberCases) %>%
  left_join((ConfProbCases %>%
               mutate(day = day(AttributionDate)) %>%
               filter(year(AttributionDate)<year(Sys.Date())|
                      month(AttributionDate)<month(Sys.Date())
                      |
                        ((month(AttributionDate)==month(Sys.Date())&(day<30)))
                      ) %>%
               group_by(age_group) %>%
               summarise(TotalCases = n())), by = "age_group") %>%
  replace(., is.na(.), 0) %>%
  mutate(RecoveredPct = round(Recovered/TotalCases*100,2),
         HospitalPct = round(Hospitalized/TotalCases*100,2),
         ActivePct = round(Active/TotalCases*100,2),
         DiedPct = round(Died/TotalCases*100,2)) %>%
plot_ly(x = ~age_group,
        y = ~RecoveredPct,
        type = "bar",
        name = "Recovered",
        color = I("#F2BF4C")) %>%
add_trace(y = ~HospitalPct,
          type = "bar",
          name = "Hospitalized",
          color = I("#477691")) %>%
add_trace(y = ~DiedPct,
          type = "bar",
          name = "Died",
          color = I("#BB4628")) %>%
add_trace(y = ~ActivePct,
          type = "bar",
          name = "Active",
          color = I("#4E2B1F")) %>%
  layout(margin = list(t = 45),
         title = list(text = "Case Outcomes by Age, All Cases through Most Recent Complete Month",
                      yref = "container",
                      yanchor = "top",
                      pad = list(t = 15),
                      y = 1),
         xaxis = list(title = "Age Group"),
         yaxis = list(title = "Proportion"),
         barmode = "stack",
         legend = list(orientation = 'h', y=-.25),
         font = list(family = "Arial", size = 12))
  
```


